---
title: "Intro to vim"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Vim 
![Vim Logo](images/VimLogo.svg)

### What is it?
Vim is a highly configurable text editor built to enable efficient text editing. 
It is an improved version of the vi editor distributed with most UNIX systems. 
Vim is distributed free as charityware. 
[source](http://www.vim.org/)

### When do I use it?
- Quickly updating a file without opening an IDE.

### When don't I use it?
- If I want to sit down and work on a project for awhile.
- If I want to use my mouse.

### History
"When Bram Moolenaar had bought an Amiga computer, he wanted to use the editor he learned on Unix. 
Since there was no good Vi for the Amiga, he started with the best that was available (a program called Stevie) and started improving it.
At first, his goal was to imitate Vi. 
Later new functionality was added, and by version 1.22 Vim included more features than Vi. 
That time it was renamed from Vi IMitation to Vi IMproved."
[source](https://medium.com/@jovica/the-history-of-vim-b707758fb54f)

### Bare Minumum Knowledge to use Vim
In my experience you can get 90% of Vim's advantages with just these simple commands.
<i>I'm sure this is sacrilege to Vim power users...but I'm not one of them yet</i>

Two main Modes:
- Command mode: is where you can run commands. This is the default mode in which Vim starts up.
- Insert mode: is the mode where you insert/write your text.

| Command         | Action                                                |
| :---            | :---                                                  |
| vim test_file.R | create an empty file or open an existing file         |
| Up Arrow        | move your cursor up a line in Command or Insert mode  |
| Down Arrow      | move your cursor down a line in Command or Insert mode|
| Left Arrow      | move your cursor up a line in Command or Insert mode  |
| Right Arrow     | move your cursor up a line in Command or Insert mode  |
| Esc             | enter Command mode                                    |
| i               | enter Insert mode                                     |
| u               | undo (for when things go wrong                        |
| :q!             | Quit without saving (for when things go really wrong  |
| :x              | Write file (if changes have been made) and exit       |




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
